An Example Using the Tufte Style

### 2016-10-16 lists_conversion_experience.rmd
messing up the formatting!

@@

![Realtime infrastructure and its limits](~/lists/figure/hadoop.png)

@@

```{r biscuits, echo=FALSE, cache=TRUE}
    library(dplyr)
    library(ggplot2)
    library(readr)
    bisc = read_tsv('data/biscuits.csv')
    bisc %>% select(price, name)  %>% order(price, decreasing=TRUE)    
    bisc[order(bisc$price, decreasing=TRUE), c('name','price')]
```
We can imagine this in terms of biscuits. A customer's recommendation list might already include `r bisc$name[10]`.  The 'self-learning substitution model' might be able to substitute something in that list that is of higher value, either because it is bigger or more expensive.

>>>>

```{r setup, cache=FALSE, include=FALSE}
library(knitr)
output <- opts_knit$get("rmarkdown.pandoc.to")
opts_chunk$set(warnings=FALSE)
opts_chunk$set(messages=FALSE)
```

@@

![Realtime infrastructure and its limits](figure/hadoop.png)

@@

```{r biscuits, echo=FALSE, cache=TRUE}
    library(dplyr)
    library(ggplot2)
    library(readr)
    bisc = read_tsv('data/biscuits.csv')
    bisc[order(bisc$price, decreasing=TRUE), c('name','price')]
```
We can imagine this in terms of biscuits. A customer's recommendation list might already include `r bisc$name[10]`.  The 'self-learning substitution model' might be able to substitute something in that list that is of higher value, either because it is bigger or more expensive.
